\documentclass[nooutcomes]{ximera}

\input{../preamble.tex}

\title{Sums and products combined, oh my!}

\begin{document}
\begin{abstract}
Here we investigate a new way to combine numbers.
\end{abstract}
\maketitle

\paragraph{The setting:}

Suppose you wrote the numbers $1,2,3,\dots,100$ on a chalkboard. You
may take any two numbers, erase them, and then add the sum of their
sum and their product to the list.

\begin{problem}
     Write down as many mathematical questions as you can for this
     setting. After you have your questions, label them as ``Level
     1,'' ``Level 2,'' or ``Level 3'' where:
\begin{description}
\item[Level 1] Means you know the answer, or know exactly how to do
  this problem.
\item[Level 2] Means you think you know how to do the problem.
\item[Level 3] Means you have no idea how to do the problem.
\end{description}
\begin{freeResponse}
  Here are some example questions:
  \paragraph{Level 1}
  \begin{enumerate}
    \item Given two positive numbers, if we perform the process on
      these numbers will the result always be larger than the initial
      two numbers?
    \item If we do this process with a number and zero, what will be
      the result?
    \item Given a list of $2$ numbers, after performing the processes
      once, how many numbers are in the list?
    \item Given a list of $100$ numbers, after perfomring the process
      once, how many numbers are in the list?
    \item If we perform the process enough times, will we always end
      with one number?
    \item Given a list of $100$ numbers, how many times do we need to
      perfom th e process to end with exaclty $1$ number?
    \item Given a list of positive numbers, can we choose which two
      will give us the largest result after perfoming the process?
    \item Given a list of positive numbers, can we choose which two
      will give us the smallest result after perfoming the process?
    \item If we think of the process as a binary operation, call it
      $\pt$, is it commutative?
    \item What is $1 \pt 1$?
  \end{enumerate}

  \paragraph{Level 2}
  \begin{enumerate}
    \item Given two numbers $a$ and $b$, possibly positive or negative
      or zero, will the result ever be smaller than $a$ or $b$?
  \end{enumerate}

  \paragraph{Level 3}
  \begin{enumerate}
    \item
  \end{enumerate}
  
\end{freeResponse}
\end{problem}


%% \begin{problem}
%% In class we came up with several questions involing this setting. State three of them. 
%% \begin{freeResponse}
%% \end{freeResponse}
%% \end{problem}

%% \begin{problem}
%%   With this setting, we made up a new operation $\pt$ where
%%   \[
%%   a\pt b = a+b + ab
%%   \]
%%   What is
%%   \[
%%   a\pt b\pt c = \answer{a+b+c+ab+ac+bc+abc}
%%   \]
%% \end{problem}

%% \begin{problem}
%% We showed that $\pt$ is \textbf{commutative}, which means
%% \begin{multipleChoice}
%%   \choice[correct]{$a\pt b = b\pt a$}
%%   \choice{$((a\pt b)\pt c) = a(\pt (b\pt c))$}
%% \end{multipleChoice}
%% \end{problem}

%% \begin{problem}
%% We showed that $\pt$ is \textbf{associative}, which means
%% \begin{multipleChoice}
%%   \choice{$a\pt b = b\pt a$}
%%   \choice[correct]{$((a\pt b)\pt c) = a(\pt (b\pt c))$}
%% \end{multipleChoice}
%% \end{problem}

%% \begin{problem}
%% Finally we encoutered several squences of numbers including
%% \begin{align*}
%%   &\{ 1, 3, 7, 15, 63,\dots\}\\
%%   &\{ 2, 4, 8, 16, 64,\dots\}\\
%%   &\{ 1, 5, 23, 119, 719,\dots\}\\
%%   &\{ 1, 2, 6, 24, 120,\dots\}
%% \end{align*}
%% Look these sequences up at \link{https://oeis.org/}{https://oeis.org/}. Find something intersting at the OEIS and tell us about it.
%% \begin{freeResponse}
%% \end{freeResponse}
%% See you next Tuesday!
%% \end{problem}


\end{document}
